---
title: "MXNET_NNET_RBFDDA_ESSSEMBLE_WITH_KNN_ALGORITHM"
output: html_notebook
---
# REFERENCES
# https://cran.r-project.org/web/packages/caret/caret.pdf
# https://cran.r-project.org/web/packages/ROSE/ROSE.pdf
# https://cran.r-project.org/web/packages/nnet/nnet.pdf
# https://s3.amazonaws.com/mxnet-prod/docs/R/mxnet-r-reference-manual.pdf
# https://cran.r-project.org/web/packages/RSNNS/RSNNS.pdf
# https://machinelearningmastery.com/machine-learning-ensembles-with-r/
# https://rpubs.com/zxs107020/370699
# https://cran.r-project.org/web/packages/caretEnsemble/vignettes/caretEnsemble-intro.html
# https://www.analyticsvidhya.com/blog/2016/12/practical-guide-to-implement-machine-learning-with-caret-package-in-r-with-practice-problem/


# LOAD THE REQUIRED LIBRARY
```{r}
require(caret)
require(DMwR)
require(ROSE)
require(caretEnsemble)
```
# SET WORKING PATH AND READ CSV 
```{r}
setwd("~/SANDY/workbench/1_R/2_NOTEBOOK/V1")
clean_data_orginal <- read.csv("NHANES_2013-2014_Subset-unbalanced_removedNA_recode1Yes0No1Male0Female-2.csv",header = TRUE)
```
#SET LEVELS AND TARGET VARIABLE FACTOR
```{r}
clean_data_orginal$MCQ160E_HeartAttack_MyocardialInfarction[clean_data_orginal$MCQ160E_HeartAttack_MyocardialInfarction==1] <- "Yes"
clean_data_orginal$MCQ160E_HeartAttack_MyocardialInfarction[clean_data_orginal$MCQ160E_HeartAttack_MyocardialInfarction==0] <- "No"
clean_data_orginal$MCQ160E_HeartAttack_MyocardialInfarction <- as.factor(clean_data_orginal$MCQ160E_HeartAttack_MyocardialInfarction)
```
# DIVIDE THE DATA INTO TRAINING AND VALIDATION DATASET
```{r}
set.seed(43)
splitIndex_org  <- createDataPartition(clean_data_orginal$MCQ160E_HeartAttack_MyocardialInfarction, p =0.80, list = FALSE)
train_data_org     <- clean_data_orginal[ splitIndex_org,]
test_data_org      <- clean_data_orginal[-splitIndex_org,]
```
# BALANCING DATA USING ROSE 
```{r}
train_data_org$MCQ160E_HeartAttack_MyocardialInfarction <- as.factor(train_data_org$MCQ160E_HeartAttack_MyocardialInfarction)
train_data_org_balanced <- ROSE(MCQ160E_HeartAttack_MyocardialInfarction~.,  data=train_data_org,N=10000, p=0.2, seed = 1234)$data 
```
# SETTING TRAINING CONTROL SETTING
```{r}
# K-fold cross validation with k=10
train_ctrl <- trainControl("cv", number = 10,classProbs = TRUE, savePredictions = TRUE)
```

# FITTING NNET MODEL
```{r}
modelLookup(model='nnet')
```
```{r}
set.seed(12345)
nnet_grid <- expand.grid(size=3, decay=0.9)#
# Size is the number of units in hidden layer (nnet fit a single hidden layer neural network).
# Decay is the regularization parameter to avoid over-fitting. 
set.seed(12346)
nnet_model <- caret::train(MCQ160E_HeartAttack_MyocardialInfarction ~., 
                         data = train_data_org_balanced, 
                         method = 'nnet', 
                         preProcess = c('center', 'scale'), 
                         trControl = train_ctrl, 
                         tuneGrid = nnet_grid, 
                         trace = TRUE, 
                         linout = FALSE) 
```
# CONFUSION MATRIX - NNET - TRAINING 
```{r}
nnet_tr_results <- predict(nnet_model, newdata=train_data_org_balanced)
nnet_tr_confusionmatrix <- caret::confusionMatrix(nnet_tr_results, train_data_org_balanced$MCQ160E_HeartAttack_MyocardialInfarction,positive="Yes")
print(nnet_tr_confusionmatrix) 
```
# CONFUSION MATRIX - NNET - TEST
```{r}
nnet_t_results <- predict(nnet_model, newdata=test_data_org)
nnet_t_confusionmatrix <- caret::confusionMatrix(nnet_t_results, test_data_org$MCQ160E_HeartAttack_MyocardialInfarction,positive="Yes")
print(nnet_t_confusionmatrix) 
```
# SAVE NNET MODEL 
```{r}
saveRDS(nnet_model,"nnet_model.rds")
```

# FITTING RBF MODEL WITH DYNAMIC DECAY ADJUSTMENT (DDA) ALGORITHM
```{r}
modelLookup(model='rbfDDA')
```
```{r}
set.seed(12345)
rbf_grid = expand.grid(negativeThreshold=0.0000000000001)#0.0000000000001
set.seed(12346)
system.time(rbf_model <- caret::train(MCQ160E_HeartAttack_MyocardialInfarction ~., 
                          data = train_data_org_balanced, 
                          method = 'rbfDDA', 
                          preProcess = c('center', 'scale'), 
                          trControl = train_ctrl, 
                          tuneGrid = rbf_grid, 
                          trace = TRUE, 
                          linout = FALSE))

```
#CONFUSION MATRIX - RBF - TRAINING 
```{r}
rbf_tr_results <- predict(rbf_model, newdata=train_data_org_balanced)
rbf_tr_confusionmatrix <- caret::confusionMatrix(rbf_tr_results, train_data_org_balanced$MCQ160E_HeartAttack_MyocardialInfarction,positive="Yes")
print(rbf_tr_confusionmatrix) 
```
#CONFUSION MATRIX - RBF - TEST
```{r}
rbf_t_results <- predict(rbf_model, newdata=test_data_org)
rbf_t_confusionmatrix <- caret::confusionMatrix(rbf_t_results, test_data_org$MCQ160E_HeartAttack_MyocardialInfarction,positive="Yes")
print(rbf_t_confusionmatrix) 
```
# SAVE RBF MODEL 
```{r}
saveRDS(rbf_model, "rbf_model.rds")
```

# FITTING MXNET MODEL
```{r}
require(mxnet)
modelLookup(model='mxnet')
```
```{r}
set.seed(12345)
mxnet_grid = expand.grid(layer1=750,#250
                         layer2=350,#180
                         layer3=150,#120
                         learning.rate=0.005,
                         momentum=0.98,#0.98
                         dropout=0.000001,#0.001
                         activation='relu')
set.seed(12346)
mxnet_model <- caret::train(MCQ160E_HeartAttack_MyocardialInfarction ~., 
                            data = train_data_org_balanced, 
                            method = 'mxnet', 
                            preProcess = c('center', 'scale'), 
                            trControl = train_ctrl, 
                            tuneGrid = mxnet_grid)
```
# CONFUSION MATRIX - MXNET - TRAINING 
```{r}
mxnet_tr_results<- predict(mxnet_model, newdata=train_data_org_balanced)
mxnet_tr_confusionmatrix <- caret::confusionMatrix(mxnet_tr_results, train_data_org_balanced$MCQ160E_HeartAttack_MyocardialInfarction,positive="Yes")
print(mxnet_tr_confusionmatrix) 
```
# CONFUSION MATRIX - MXNET - TEST
```{r}
mxnet_t_results<- predict(mxnet_model, newdata=test_data_org)
mxnet_t_confusionmatrix <- caret::confusionMatrix(mxnet_t_results, test_data_org$MCQ160E_HeartAttack_MyocardialInfarction,positive="Yes")
print(mxnet_t_confusionmatrix) 
```
# SAVE MXNET MODEL 
```{r}
saveRDS(mxnet_model,"mxnet_model.rds")
```

# CREATING ESSEMBLE MODELLING OF NNET, MXNET, RBFDDA with K_NEAREST NEIGBOUR ALGORITHM
```{r}
# SETTING TRAINING CONTROL SETTING
# K-fold cross validation with k=10
set.seed(12345)
train_ctrl_essemble <- trainControl("cv", 
                                    number = 10, 
                                    #search = "grid", 
                                    savePredictions ='final', 
                                    #index = createFolds(train_data_org_balanced$MCQ160E_HeartAttack_MyocardialInfarction, 10), 
                                    #summaryFunction = twoClassSummary, 
                                    classProbs = TRUE)
                                    #verboseIter = TRUE)

```
```{r}
set.seed(12346)
# Creating essemble
# using the tune parameter indentified earlier we create a caret stack list for the models. 

require(mxnet)
model_list <- caretList( MCQ160E_HeartAttack_MyocardialInfarction ~., 
                         data = train_data_org_balanced, 
                         preProcess = c('center', 'scale'), 
                         trControl= train_ctrl_essemble,
                         tuneList=list(  nnet=caretModelSpec(method='nnet',   tuneGrid=expand.grid(size=3, decay=0.9)),
                                         rbfDDA=caretModelSpec(method='rbfDDA', tuneGrid=expand.grid(negativeThreshold=0.0000000000001)), 
                                          mxnet=caretModelSpec(method='mxnet',  tuneGrid=expand.grid(layer1=750,#250
                                                                                                   layer2=350,#180
                                                                                                    layer3=150,#120
                                                                                                    learning.rate=0.005,
                                                                                                    momentum=0.98,#0.98
                                                                                                    dropout=0.000001,#0.001
                                                                                                    activation='relu'))))
```
```{r}
saveRDS(model_list,"model_list.rds")
```
```{r}
#Load Prerun Model from the screen above.
model_list <- readRDS("model_list.rds")
```
```{r}
# Create stack list essemble with KNN algorithm.
set.seed(12347)
stackControl <-  trainControl(method = "repeatedcv", number = 10, repeats = 3,savePredictions = TRUE, classProbs = TRUE, verboseIter = TRUE)
set.seed(123481)
stack <- caretStack(model_list, method = "knn", metric = "Accuracy", trControl = stackControl) #rpart 
```
```{r}
#Find the confusion matrix of essemble with test data. 

stack_test_preds_results <- predict(stack, newdata=test_data_org)
stack_test_preds_confusionmatrix <- caret::confusionMatrix(stack_test_preds_results, test_data_org$MCQ160E_HeartAttack_MyocardialInfarction,positive="Yes")
```
```{r}
print(stack_test_preds_confusionmatrix) 
```



```{r}
rbf_model <-readRDS("rbf_model.rds")
nnet_model <-readRDS("nnet_model.rds")
mxnet_model <-readRDS("mxnet_model.rds")
model_list <-readRDS("model_list.rds")

```












